### 2020-09-28 paper_27_09_2020/paper_27_09_2020.tex
update

\documentclass[12pt,a4paper]{article} %437
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\makeatletter
\makeatother
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
%\usepackage[dvips]{graphicx, color}
\usepackage{subfigure}
\usepackage[skins,listings,breakable]{tcolorbox}

@@

\setlength\topmargin{-1.5cm} \setlength\oddsidemargin{0.0cm}
\setlength\evensidemargin{0.0cm} \setlength{\textwidth}{16cm}
\setlength{\textheight}{25cm}

@@

@@

\begin{center}
\section*{\centerline {A new family of continuous distributions: properties and applications}}
\vspace{0.3in}
{\large Gauss M. Cordeiro$^a$ , Maria do Carmo$^a$ and Pedro Rafael D. Marinho$^b$}\\
%\vspace{0.3in}
%First Version: 27 July 2010\\
%\vspace{0.1in}
%This Version: 27 January 2011\\
\end{center}

\begin{abstract}\noindent
This article introduces generalized beta-generated (GBG) distributions. Sub-models
include all classical beta-generated, Kumaraswamy-generated and exponentiated
distributions. They are maximum entropy distributions under three intuitive
conditions, which show that the classical beta generator skewness parameters
only control tail entropy and an additional shape parameter is needed to add entropy
to the center of the parent distribution. This parameter controls skewness
without necessarily differentiating tail weights. The GBG class also
has tractable properties: we present various expansions for moments,
generating function and quantiles. The model parameters
are estimated by maximum likelihood and the usefulness of the new class
is illustrated by means of some real data sets.
\end{abstract}

\vspace{0.5in}
\noindent {\bf Key Words}: \\ \\
%\noindent {\bf JEL Codes}: C16, G1 \\ \\
\noindent $^{a}$  Department of Statistics, Federal University of Pernambuco, Recife, Brazil.\\
\noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
E-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\

@@

There has been an increased interest in developing generalized families of distributions by
introducing additional shape parameters to a baseline cumulative distribution. This mechanism has
proved to be useful to make the generated distributions more flexible especially for studying tail properties
than existing distributions and for improving their goodness-of-fit statistics
to the data under study.

Let $G(x)$ be the cumulative distribution function (CDF) of a
baseline distribution and $g(x)=dG(x)/dx$ be the associated
probability density function (PDF) depending on a parameter vectot $\eta$. We present a generalized family
with two additional shape parameters by transforming the CDF $G(x)$
according to two sequential important gene\-rators. These families are important for modeling data
in several engineering areas. Many special distributions in these families are discussed by Tahir
and Nadarajah (2015).

Marshall and Olkin (1997) pioneered a general method to expand
a distribution G by adding an extra shape parameter.
The CDF of their family (for $\theta>0$) is
\begin{equation}\label{CDF_MO}
F_{\text{MO-G}}(x)=\frac{G(x)}{\theta+(1-\theta)G(x)}=\frac{G(x)}{1-(1-\theta)[1-G(x)]},\quad x \in \mathbb{R}.
\end{equation}

The density function corresponding to (\ref{CDF_MO}) is
\begin{equation}\label{densityMO}
f_{\text{MO-G}}(x)=\frac{\theta g(x)}{[\theta+(1-\theta)G(x)]^{2}},\quad x \in \mathbb{R}.
\end{equation}
For $\theta = 1$, $f_{\text{MO-G}}(x)$ is equal to $g(x)$ and, for different values of
$\theta$, $f_{\text{MO-G}}(x)$ can be more flexible than $g(x)$.
The extra parameter $\theta$ is called ``tilt parameter'', since
the HRF of the MO-G family is shifted below ($\theta> 1$)
or above ($0<\theta<1$) of the baseline HRF. Equation \eqref{densityMO} provides a useful
mechanism to generate new distributions from existing ones. The advantage of this approach
for constructing new distributions lies in its flexibility to model
both monotonic and non-monotonic HRFs even when the baseline HRF may be
monotonic. Tahir and Nadarajah (2015, Table 2) presented thirty distributions belonging to
the $\text{MO-G}$ family. Further, this family is easily generated from the baseline QF by
$Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.

Marshall and Olkin considered the exponential and Weibull distributions for the baseline G and derived some
structural properties of the generated distributions. The special case that G is an exponential distribution
refers to a two-parameter competitive model to the Weibull and gamma distributions.
A simple interpretation of (\ref{CDF_MO}) can be given as follows. Let $T_1,\ldots,T_N$ be a sequence
of independent and identically distributed (i.i.d.)~random variables with survival function (SF)
$\overline{G}(x)=1-G(x)$, and let $N$ be a positive integer
random variable independent of the $T_i$'s defined by the probability generating function (PGF) of a
geometric distribution with parameter $\theta$, say $\tau(z;\theta)=\theta z\,[1-(1-\theta)z]^{-1}$.
Then, the inverse of $\tau(z;\theta)$ becomes $\tau^{-1}(z;\theta)=\tau(z;\theta^{-1})$. We can verify that
equation \eqref{CDF_MO} comes from $1 - F_{\text{MO-G}}(x)=\tau(\overline{G}(x);\theta)$ for $0<\theta<1$ and
$1-F_{\text{MO-G}}(x)=\tau(\overline{G}(x);\theta^{-1})$ for $\theta>1$. For both cases, $1-F_{\text{MO-G}}(x)$
re\-presents the SF of $\min\{T_1,\ldots,T_N\}$, where $N$ has
PGF $\tau(z;\cdot)$ with probability parameters $\theta$ or $\theta^{-1}$.

Zografos and Balakrishnan (2009) and Risti\'{c} and Balakrishnan (2011)
defined the gamma-G ($\Gamma$-G) family with an extra shape parameter $a>0$ by
the CDF (for $x \in \mathbb{R}$)
\begin{eqnarray}\label{CDF_Ga}
F_{\Gamma\text{-G}}(x)=\gamma_1\left( a, -\log \left[1-G(x)\right]\right)
=\frac{\displaystyle 1}{\displaystyle \Gamma(a)}\,\gamma\left( a, -\log \left[1-G(x)\right]\right),
\end{eqnarray}
where $\gamma(a,z)=\int_0^{z} t^{a-1}\,\rm{e}^{-t}dt$ is the incomplete gamma function and
 $\gamma_1(a,z)= \gamma(a,z)/\Gamma(a)$ is the incomplete gamma function ratio.
The PDF of the $\Gamma$-G family takes the form
\begin{eqnarray}\label{PDF_Ga}
\displaystyle
f_{\Gamma\text{-G}}(x)=\frac{\displaystyle 1}{\displaystyle \Gamma(a)} \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x),
\quad x \in \mathbb{R}.
\end{eqnarray}
Each new $\Gamma$-G distribution can be determined from a given baseline distribution.
For $a=1$, the G distribution is a basic exemplar of the $\Gamma$-G family.

Zografos and Balakrishnan (2009) and Risti\'{c} and Balakrishnan (2011)
presented a physical motivation for the $\Gamma$-G family: if $X_{L(1)},\ldots, X_{L(n)}$ are lower record values
from a sequence of independent random variables with common PDF $g (\cdot)$, then the PDF of the $n$th lower
record value has the form (\ref{PDF_Ga}). If $Z$ is a gamma random variable with unit scale
parameter and shape parameter $a>0$, then $X=Q_G(1-\rm{e}^{Z})$ has density (\ref{PDF_Ga}). So,
the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.

The rest of the paper is organized as follows. Section \ref{sec:MOGaG} describes the distribution and density
of the new class of distributions called the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G) family  by combining the above generators.
We also present some special models. The maximum likelihood estimation of the model parameters of the new family is
described in Section \ref{estimation}. In Section \ref{applications}, we provide some empirical applications to illustrate
the potentiality of the proposed family. A variety of theoretical properties are considered in Section \ref{properties}.
Finally, conclusions are noted in Section \ref{conclusions}.

@@

Let $X\sim$MO-$\Gamma$-G denote a random variable having the MO-$\Gamma$-G family with two extra shape parameters $\theta>0$ and $a>0$
and the baseline vector $\eta$. By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of $X$ has the form
\begin{equation}\label{CDF_MO-Gamma-G}
F_{X}(x)=\frac{\gamma_1\left( a, -\log \left[1-G(x)\right]\right)}{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)},\quad x \in \mathbb{R}.
\end{equation}

By differentiating (\ref{CDF_MO-Gamma-G}), we can write the PDF of $X$ as
\begin{equation}\label{CDF_MO-Gamma-G}
f_{X}(x)=\frac{\theta  \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)\right\}^{2}},\quad x \in \mathbb{R}.
\end{equation}

\begin{landscape}
\begin{table}[htbp]\label{tabspecial1}
\centering
\begin{tabular}{c|c|c}
\hline
\textbf{Distribution} & \textbf{Baseline CDF} & \textbf{Generated PDF}  \\
\hline
{} & {} & {} \\
\textbf{Normal} &  $G(x)=\Phi(x)$ & $f_{X}(x)=\frac{\theta  \left\{ -\log[1-\Phi(x)] \right\}^{a-1}\, \phi(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Logistic} &  $G(x)=\frac{1}{1+\rm{e}^{-x}}$ & $f_{X}(x)=\frac{\theta\,\rm{e}^{-x}\, \left\{ -\log[1-(1+\rm{e}^{-x})^{-1}] \right\}^{a-1}}{\Gamma(a)\,(1+\rm{e}^{-x})^{2}\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-(1+\rm{e}^{-x})^{-1}\right]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\textbf{Gumbel} &  $G(x)=1-\exp(-\rm{e}^x)$ & $f_{X}(x)=\frac{\theta \, \exp(a \,x-  \rm{e}^x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a, \rm{e}^{x}\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Log-Normal} &  $G(x)=\Phi(\log x)$ & $f_{X}(x)=\frac{\theta\,\phi(\log x)\,  \left\{ -\log[1-\Phi(\log x)] \right\}^{a-1}}{\Gamma(a)\,x\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(\log x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Exponential} &  $G(x)=1-\exp(-\lambda x),\,\lambda>0$ & $f_{X}(x)=\frac{\theta\,\lambda^{a}\,x^{(a-1)}\, }{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a,\lambda x\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Weibull} &  $G(x)=1-\exp(-(\lambda x)^\gamma),\,\lambda,\gamma>0$ & $f_X(x)=\frac{\theta\,\gamma\lambda^{a\,\gamma}x^{a\,\gamma-1}\exp\{-(\lambda\,\gamma)^\gamma\}}{\Gamma (a)\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\}^2}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Gamma} &  $G(x)=\gamma_1(\alpha,\beta x),\,\alpha,\,\beta>0$ & $f_{X}(x)=\frac{\theta\,\beta^{\alpha}\,x^{\alpha-1}\,\rm{e}^{-\beta x}\,\left\{ -\log[1-\gamma_1(\alpha,\beta x)] \right\}^{a-1}}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\gamma_1(\alpha,\beta x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\                                                                                                                                                                                                                                                                           \hline
\textbf{Pareto} &  $G(x)=1-\frac{1}{(1+x)^\nu},\,\nu>0$ & $f_{X}(x)=\frac{\theta \, \rm{e}^{-x}\, \left[\nu\log(1+x)\right]^{a-1}\, g(x)}{\Gamma(a)\,(1+\rm{e}^{-x})^2\,\left\{\theta+(1-\theta)\gamma_1\left( a, \nu\log[1+x]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
{} & {} & {} \\
\hline
\end{tabular}
\caption{Special Distributions in the  MO-$\Gamma$-G family.}
($\Phi(x)$ and $\phi(x)$ denote the standard normal distribution and density\\ functions and $\gamma_1(a,z)$ is the incomplete gamma function ratio).
\end{table}
\end{landscape}

Figure \ref{formas} shows the performance of the density and hazard functions of the Marshall-Olkin Gamma Weibull (MO-$\Gamma$-W, for short). Note that this extension of the Weibull distribution provides more flexibility for density and hazard shapes.

\begin{figure}[h!]
\begin{center}
(a)\hspace{3.5cm} (b)\\
\includegraphics[scale=.3]{density.pdf}
\includegraphics[scale=.3]{hazard.pdf}\\
\vspace{-0.5cm}
\caption{(a) Curves for the MO-$\Gamma$-W density; (b) Curves for the MO-$\Gamma$-W hazard;\label{formas}}
\end{center}
\end{figure}

\subsection{Quantile Function}\label{QuantFunc}

We can easily invert the cdf \eqref{CDF_MO-Gamma-G} to express the MOGa-G
quantile function (qf), say $x=Q_{X}(u)=G^{-1}(u)$, in terms of the baseline 
qf $Q_G(u)$. Let $u$ be a uniform $U(0,1)$ random variate. By using \eqref{CDF_MO-Gamma-G}
and letting $z=\gamma_{1}\left(a, -\log[1-G(x)]\right)$, we obtain $z=z(u)=\theta u/[1-(1-\theta)u]$. 
Then, the qf of $X$ has the form $x=Q_G\left(1-\rm{e}^{-v}\right)$, where $v=v(z)$ is a random variate generated
from a gamma distribution (with shape parameter $\alpha$ and unit scale parameter) corresponding to the quantile $z$. 
This scheme is useful because of the existence of fast generators for uniform and gamma 
random variables.

@@

The  MO-$\Gamma$-G family mentioned previously can be  fitted to real data sets using the {\it AdequacyModel}
package for the {\sf R} statistical computing environment ({\tt https://www.r-project.org/}).
An important advantage of this packa\-ge is that it is not necessary to define
the log-likelihood function and that it computes the maximum likelihood estimates (MLE), their standard errors and the formal statistics
presented in the nest section. We only need to provide the PDF and CDF of the distribution to be fitted to a data set.
This {\it AdequacyModel} package uses the PSO (particle swarm optimization) method obtained by traditional global search approaches
such as the quasi-Newton BFGS, Nelder-Mead and simulated-annealing methods to maximized the log-likelihood function. This
method does not require initial values. More
details are available at {\tt https://rdrr.io/cran/AdequacyModel/}.

Here, we consider estimation of unknown parameters of the MO-$\Gamma$-$G$ distribution by the method of maximum likelihood. If $x$ is one observation from \ref{} and $\etn$ a q-vector parameter vector specifying $G(.)$, thus the log-likelihood function, say $\log L=\log L(a,\theta,\etn)$ is
\begin{align}\ell (\boldsymbol{\Theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n{\log(x_i)}-n\log[\Gamma(a)] \nonumber \\ & -2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}
\end{align}

\section{Simulation}\label{sec:simulation}

Due to the probable absence of maximum likelihood estimators - MLE in closed form for distributions belonging to the MO-$\Gamma $-G family, it is necessary to understand the precision of the estimates obtained numerically. For that, we chose to study the bias of the estimators of the MO-$\Gamma$-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution, in which $ G \sim \mathrm {Dagum} (\alpha, \beta, p) $, for different sample sizes, being (10, 20, 60, 100, 200, 400, 600, 1000, 2000, 5000, 10000, 20000, 30000 and 500000).

The simulations considered 10,000 Monte-Carlo - MC iterations for each of the sample sizes to which the numerical estimates were obtained by the BFGS method. Table \ref{tab:bias} shows that the BFGS method behaves well as the sample size grows. This is theoretically expected, however, in practice, difficulties can be faced in other families of distributions due to complications in the likelihood function.

All simulations can be reproduced using the code in Annex \ref {ap:simulation}. The MC simulations are parallelized and are able to use all threads available by a multicore processor, thus making them more computationally efficient and consequently requiring less time to complete. The simulations were performed on a computer with an Intel Core i5-8265U processor with 8 threads working at a maximum frequency of 3.90 GHz, requiring, on these hardware, a time of 14.36 hours to perform all simulations.

>>>>

\documentclass[12pt,a4paper]{article} %437
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}
\makeatletter
\makeatother
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{float}
\usepackage{listings}
%\usepackage[dvips]{graphicx, color}
%\usepackage{subfigure}
%\usepackage[skins,listings,breakable]{tcolorbox}

@@

\setlength\topmargin{-1.5cm} \setlength\oddsidemargin{0.0cm}
\setlength\evensidemargin{0.0cm} \setlength{\textwidth}{15cm}
\setlength{\textheight}{25cm}

@@

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=cyan,
}

\urlstyle{same}

@@

\begin{center}
\section*{\centerline {A new family of distributions: properties and applications}}
\vspace{0.3in}
{\large Gauss M. Cordeiro$^a$ , Maria do Carmo S. Lima$^a$ and Pedro Rafael D. Marinho$^b$}\\
%\vspace{0.3in}
%First Version: 27 July 2010\\
%\vspace{0.1in}
%This Version: 27 January 2011\\
\end{center}

\begin{abstract}\noindent
This article introduces a new family by combining the Marshall and Olkin-G and Gamma-G classes. The family has only two
extra shape parameters and can be a better alternative than other existing classes of distributions. Simulations are performed to verify the
consistency of the estimators. Its flexibility is shown using two real data sets.
\end{abstract}

\vspace{0.5in}
\noindent {\bf Key Words}:  Distribution family;  mathematical properties; simulations; applications.\\ \\
%\noindent {\bf JEL Codes}: C16, G1 \\ \\
\noindent $^{a}$  Department of Statistics, Federal University of Pernambuco, Recife, Brazil.\\
\noindent $^{b}$ Department of Statistics, Federal University of Paraíba, João Pessoa, Brazil.\\
E-mail:\emph{gausscordeiro@de.ufpe.br, maria@de.ufpe.br, pedro.rafael.marinho@gmail.com} \\

@@

The mechanism by adding shape parameters to a baseline distribution has
proved to be useful to make the generated distributions more flexible especially for studying tail
properties than existing distributions and for improving their goodness-of-fit statistics
to the data under study.

Let $G(x)$ be the cumulative distribution function (CDF) of a
baseline distribution and $g(x)=dG(x)/dx$ be the corresponding  probability density function (PDF) depending on a
parameter vectot $\eta$. A generalized family are presented
with two additional shape parameters by transforming the CDF $G(x)$
according to two sequential important gene\-rators. These families are important for modeling data
in several engineering areas. Many special distributions in these families are discussed by Tahir
and Nadarajah (2015).

The CDF of the Marshall and Olkin's (1997) ($\text{MO-G}$) family (for $\theta>0$) is
\begin{equation}\label{CDF_MO}
F_{\text{MO-G}}(x)=\frac{G(x)}{\theta+(1-\theta)G(x)}=\frac{G(x)}{1-(1-\theta)[1-G(x)]},\quad x \in \mathbb{R}.
\end{equation}

The density function corresponding to (\ref{CDF_MO}) has the form
\begin{equation}\label{densityMO}
f_{\text{MO-G}}(x)=\frac{\theta\, g(x)}{[\theta+(1-\theta)G(x)]^{2}}.
\end{equation}

For $\theta=1$, $f_{\text{MO-G}}(x)$ is equal to $g(x)$. 
Equation \eqref{densityMO} represents the PDF of the minimum of $n$ iid random variables having density $g(x)$, say $T_1,\cdots,T_N$, 
where $N$ has a geometric distribution with probability parameters $\theta$ and $\theta^{-1}$ if $0<\theta<1$ and $\theta>1$, 
respectively.

Tahir and Nadarajah (2015, Table 2) presented thirty distributions
belonging to this family. It is easily generated from the baseline quantile function (QF) by
$Q_{\text{MO-G}}(u)=Q_{G}\left(\theta u \left[\theta u+1-u\right]\right)$ for $u\in(0,1)$.

Marshall and Olkin considered the exponential and Weibull distributions for the baseline G and derived some
structural properties of the generated distributions. The special case that G is an exponential distribution
refers to a two-parameter competitive model to the Weibull and gamma distributions.

The CDF of the gamma-G ($\Gamma$-G) family (Zografos and Balakrishnan, 2009) is
\begin{eqnarray}\label{CDF_Ga}
F_{\Gamma\text{-G}}(x)=\gamma_1\left( a, -\log \left[1-G(x)\right]\right), \quad x \in \mathbb{R},
\end{eqnarray}
where $a>0$ is an extra shape parameter,  $\gamma_1(a,z)= \gamma(a,z)/\Gamma(a)$ is the incomplete gamma function ratio
and $\gamma(a,z)=\int_0^{z} t^{a-1}\,\rm{e}^{-t}dt$.

Then, the PDF of the $\Gamma$-G family can be expressed as
\begin{eqnarray}\label{PDF_Ga}
\displaystyle
f_{\Gamma\text{-G}}(x)=\frac{\displaystyle 1}{\displaystyle \Gamma(a)} \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x).
\end{eqnarray}

Each new $\Gamma$-G distribution follows from a given baseline G.
For $a=1$, the $\Gamma$-G family reduces to G.
If $Z$ is a gamma random variable with unit scale
parameter and shape parameter $a>0$, then $W=Q_G(1-\rm{e}^{Z})$ has density (\ref{PDF_Ga}). So,
the $\Gamma$-G distribution is easily generated from the gamma distribution and the QF of G.

The remaining of the paper is addressed as follows. Section \ref{sec:MOGaG} introduces the {\it Marshall and Olkin-Gamma-G} (MO-$\Gamma$-G)
family and presents some special models. The maximum likelihood estimates (MLEs) of the parameters of the new family is addressed
in Section \ref{estimation}. Some simulations ate performed in Section \ref{sec:simulation} to estimate the biases of the MLEs. Two
empirical applications illustrate the potentiality of the proposed family in Section \ref{applications}. A variety of theoretical properties are derived
in Section \ref{properties}. Some conclusions remarks are offered in Section \ref{conclusions}.

@@

By combining Equations (\ref{CDF_MO}) and (\ref{CDF_Ga}), the CDF of the random variable $X\sim$MO-$\Gamma$-G
representing the new family is defined by
\begin{equation}\label{CDF_MO-Gamma-G}
F_{X}(x)=\frac{\gamma_1\left( a, -\log \left[1-G(x)\right]\right)}{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)},\quad x \in \mathbb{R}.
\end{equation}

By differentiating (\ref{CDF_MO-Gamma-G}), the PDF of $X$ follows as
\begin{equation}\label{PDF_MO-Gamma-G}
f_{X}(x)=\frac{\theta  \left\{ -\log[1-G(x)] \right\}^{a-1}\, g(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-G(x)\right]\right)\right\}^{2}}.
\end{equation}

The density (\ref{PDF_MO-Gamma-G}) can be interpreted from a sequence of $N$ iid random variables, say $Z_1,\cdots,Z_N$,
each one having a gamma density unit scale and shape $a>0$, assuming that $N$ (is not fixed) has a geometric 
distribution with probabilities $\theta$ and $\theta^{-1}$ for $0<\theta<1$ and $\theta>1$,
respectively. By transforming the $Z_i$'s via the baseline QF by $W_i=Q_G(1-\rm{e}^{Z_i})$
(for $i-1,\ldots,N$), Equation \eqref{densityMO} is defined the PDF of the minimum $W_1,\cdots,W_n$. 
Making this double composition of the two generators, the proposed family absorbs the impacts of two different flexibilities 
on applications.

Table \ref{tabspecial1} provides some special cases of (\ref{PDF_MO-Gamma-G}), where
$\Phi(x)$ and $\phi(x)$ are the CDF and PDF of the standard normal distribution. The density and hazard functions
of the Marshall-Olkin-$\Gamma$-Weibull (MO-$\Gamma$-W) are displayed in Figure \ref{formas}, which provide
more flexibility for these functions in relation to the baseline ones.

\vspace{0.6cm}

\begin{figure}[H]
\begin{center}
(a)\hspace{3.5cm} (b)\\
\includegraphics[scale=.3]{density.pdf}
\includegraphics[scale=.3]{hazard.pdf}\\
\vspace{-0.5cm}
\caption{(a) Curves for the MO-$\Gamma$-W density. (b) Curves for the MO-$\Gamma$-W hazard.\label{formas}}
\end{center}
\end{figure}

\vspace{0.6cm}

The CDF \eqref{CDF_MO-Gamma-G} can be easily inverted to determine the quantile function (QF) of the MO-$\Gamma$-G distribution,
say $x=Q_{X}(u)$, in terms of the baseline QF $Q_G(u)$. Let $u$ be a uniform $U(0,1)$ random variate. By using \eqref{CDF_MO-Gamma-G}
and letting $z=\gamma_{1}\left(a, -\log[1-G(x)]\right)$, it follows $z=z(u)=\theta u/[1-(1-\theta)u]$.
Then, the QF of $X$ takes the form $x=Q_G\left(1-\rm{e}^{-v}\right)$, where $v=v(z)$ is an upper point
corresponding to the quantile $z$ of a gamma density (with unit scale and shape $\alpha$).

\begin{landscape}
\begin{table}[htbp]\label{tabspecial1}
\centering
\begin{tabular}{c|c|c}
\hline
\textbf{Distribution} & \textbf{Baseline CDF} & \textbf{Generated PDF}  \\
\hline
{} & {} & {} \\
\textbf{Normal} &  $G(x)=\Phi(x)$ & $f_{X}(x)=\frac{\theta  \left\{ -\log[1-\Phi(x)] \right\}^{a-1}\, \phi(x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Logistic} &  $G(x)=\frac{1}{1+\rm{e}^{-x}}$ & $f_{X}(x)=\frac{\theta\,\rm{e}^{-x}\, \left\{ -\log[1-(1+\rm{e}^{-x})^{-1}] \right\}^{a-1}}{\Gamma(a)\,(1+\rm{e}^{-x})^{2}\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-(1+\rm{e}^{-x})^{-1}\right]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
\textbf{Gumbel} &  $G(x)=1-\exp(-\rm{e}^x)$ & $f_{X}(x)=\frac{\theta \, \exp(a \,x-  \rm{e}^x)}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a, \rm{e}^{x}\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Log-Normal} &  $G(x)=\Phi(\log x)$ & $f_{X}(x)=\frac{\theta\,\phi(\log x)\,  \left\{ -\log[1-\Phi(\log x)] \right\}^{a-1}}{\Gamma(a)\,x\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\Phi(\log x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Exponential} &  $G(x)=1-\exp(-\lambda x),\,\lambda>0$ & $f_{X}(x)=\frac{\theta\,\lambda^{a}\,x^{(a-1)}\, }{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left(a,\lambda x\right)\right\}^{2}}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Weibull} &  $G(x)=1-\exp(-(\lambda x)^\gamma),\,\lambda,\gamma>0$ & $f_X(x)=\frac{\theta\,\gamma\lambda^{a\,\gamma}x^{a\,\gamma-1}\exp\{-(\lambda\,\gamma)^\gamma\}}{\Gamma (a)\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x)^\gamma]\}^2}$ \\
{} & {} & {} \\
\hline
{} & {} & {} \\
\textbf{Gamma} &  $G(x)=\gamma_1(\alpha,\beta x),\,\alpha,\,\beta>0$ & $f_{X}(x)=\frac{\theta\,\beta^{\alpha}\,x^{\alpha-1}\,\rm{e}^{-\beta x}\,\left\{ -\log[1-\gamma_1(\alpha,\beta x)] \right\}^{a-1}}{\Gamma(a)\,\left\{\theta+(1-\theta)\gamma_1\left( a, -\log \left[1-\gamma_1(\alpha,\beta x)\right]\right)\right\}^{2}}$ \\
{} & {} & {} \\                                                                                                                                                                                                                                                                           \hline
\textbf{Pareto} &  $G(x)=1-\frac{1}{(1+x)^\nu},\,\nu>0$ & $f_{X}(x)=\frac{\theta \, \rm{e}^{-x}\, \left[\nu\log(1+x)\right]^{a-1}\, g(x)}{\Gamma(a)\,(1+\rm{e}^{-x})^2\,\left\{\theta+(1-\theta)\gamma_1\left( a, \nu\log[1+x]\right)\right\}^{2}}$\\
{} & {} & {} \\
\hline
{} & {} & {} \\
\hline
\end{tabular}
\caption{Special Distributions in the  MO-$\Gamma$-G family.}
\end{table}
\end{landscape}

@@

The  MO-$\Gamma$-G family can be  fitted to real data using the {\bf AdequacyModel} package in the {\sf R} software.
This packa\-ge does not require to define the log-likelihood function and it computes the MLEs, their standard errors (SEs)
and the formal statistics defined in Section \ref{applications}. It is necessary to provide the
PDF and CDF of the distribution to be fitted to a data set.

For example, if $x_i$ is one observation from (\ref{PDF_MO-Gamma-G}) and $\etn$ is a $q$-parameter vector specifying $G(\cdot)$,
the log-likelihood function for $\boldsymbol{\theta}^\top=(a,\theta,\etn^\top)$ from $n$ observations is
\begin{align}\label{loglik}
\ell (\boldsymbol{\theta})=&\,n\log (\theta)+n\log(\gamma)+n\, a\, \gamma \log(\lambda)+(a\gamma-1)\sum_{i=1}^n{\log(x_i)}-\lambda^\gamma\sum_{i=1}^n{\log(x_i)}\nonumber \\ &
-n\log[\Gamma(a)]-2\sum_{i=1}^n{\log\{\theta+(1-\theta)\gamma_1[a,(\lambda\,x_i)^\gamma]\}}.
\end{align}

Due to the impossibility of obtaining the MLEs in closed form, numerical methods to obtain the estimates that maximize $ \ell (\cdot) $ are necessary. Several programming languages and statistical software distributes functions and routines that make it easy to obtain numerical estimates by various interactive methods. In practice, obtaining the MLEs for the parameters that index a probability distribution are commonly obtained in this way, since the Newton and quasi-Newton methods produce satisfactory results under reasonable conditions of the object function, that is, when they do not impose conditions that disturb the convergence of the algorithms.

To obtain the MLEs, the package {\bf AdequacyModel} of the programming language {\sf R} was used, see R Core Team (2020). This library, created and maintained by one of the authors of this paper, is widely cited by several papers in the field of statistics and serves as a basis for other library implementations available on the Comprehensive R Archive Network - CRAN. With it, in particular using the function {\tt goodness.fit} it is possible to pass an implementation {\sf R} of (\ref {PDF_MO-Gamma-G}), being in charge of the function {\tt goodness.fit} obtain $\ell (\cdot)$ by returning several measures of fit adequacy as well as MLEs. Further details regarding the {\bf AdequacyModel} package can be obtained from Marinho et al. (2019).

\section{Simulations}\label{sec:simulation}

Due to the probable absence of MLEs in closed-form for distributions belonging to the MO-$\Gamma $-G family, it is necessary to examine the
precision of the estimates calculated numerically. For doing that, the biases of the estimators of the parameters of the
MO-$\Gamma$-Dagum($\theta$, $a$, $\alpha$, $\beta$, $p$) distribution are determined, where $G\sim \mathrm {Dagum} (\alpha, \beta, p)$
is the baseline distribution. All parameters are taken equal to one for different sample sizes reported in Table \ref{tab:bias}.

Ten thousand Monte Carlo simulations are performed for each sample size to examine the numerical estimates calculated by the
BFGS method. The figures in Table \ref{tab:bias} indicate that this method behaves well when the sample size increases.
This is theoretically expected. However, in practice, difficulties can be faced in other families of distributions
due to the flatness of the log-likelihood function.

All simulations can be reproduced using the script in Appendix \ref{ap:simulation}. The simulations are parallelized and able to use all threads
available by a multicore processor, thus making them more computationally efficient and consequently requiring less time to complete.
The simulations are performed on a computer with an Intel Core i5-8265U processor with 8 threads working at a maximum frequency of 3.90 GHz,
requiring, on these hardware, a time of 14.36 hours to perform all simulations. The figures in Table \ref{tab:bias} reveal that the average
biases of the MLEs could be very reduced only for $n> 2,000$.
